A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-07-23 text/manuscript.Rmd
fix study source in first sent of results

To study cancer pathways we obtained a set of 7,607 tumor samples from GDC. We
chose to start with somatic mutations in exome sequencing data because the
affected gene is known almost unambiguously. Therefore, we focused on all
missense, nonsense, frameshift, and splicing mutations. In order to minimize
bias from well-studied diseases and processes, we selected 377 Reactome pathways
[reactome.org](https://reactome.org/) of interest corresponding to basic
cellular processes and biochemical pathways, excluding gene sets that correspond
to miscellaneous categories ( _e.g._ “transcription factors”) or disease
associations ( _e.g._ “mutated in colon cancer”) and filtered our gene list on
membership in these pathways (<mark>total of x genes;</mark> see methods for
details).

>>>>

To study cancer pathways we obtained a set of 7,607 solid tumor samples from The
Cancer Genome Atlas (TCGA) through the [Genomic Data Commons (GDC)](gdc.cancer.gov)
portal. TCGA data because were
most appropriate for our study given the relative completeness of the patient
metadata, particularly for survival and staging. We chose to start with somatic
mutations in exome sequencing data because the affected target gene is known 
unambiguously. Therefore, we focused on all missense, nonsense, frameshift, and
splicing mutations. In order to minimize bias from well-studied diseases and
processes, we selected 377 Reactome pathways
[reactome.org](https://reactome.org/) of interest corresponding to basic
cellular processes and biochemical pathways, excluding gene sets that correspond
to miscellaneous categories ( _e.g._ “transcription factors”) or disease
associations ( _e.g._ “mutated in colon cancer”) and filtered our gene list on
membership in these pathways (<mark>total of x genes;</mark> see methods for
details).
